{{< var titll >}}

### 2024-10-20 abc.qmd
cont

---
title: "{{< var titll >}}"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
format:
  revealjs:
    drop:
      engine: webr
      webr:
        packages:
          - ggplot2
          - dplyr
execute: 
  cache: false
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
output: 
  html_document:
    mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
nocite: |
  @*
---

@@

2+2

>>>>

@@

[abc](https://www.arapahoevotes.gov/sites/default/files/2023-12/REDACTED_CVR_Export_20231128_0.xls)
